---
title: "iFood"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: style_dash.css
---

```{r setup, include=FALSE}
# Setting
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

# Package
library(flexdashboard)
pacman::p_load(dplyr, ggplot2, plotly, readxl)

# Data
ifood_df <- read.csv("ml_project1_data.csv", header = T)

# Miss value
ifood_df <- na.omit(ifood_df)
ifood_df$ID <- NULL

# Bở giá trị thừa
ifood_df <- ifood_df[, !names(ifood_df) %in% c("Z_CostContact", "Z_Revenue")]


color2_fill <- c("rgba(59, 134, 134, 0.5)", "rgba(121, 189, 154, 0.5)")
color2_line <- c("rgba(59, 134, 134, 1)", "rgba(121, 189, 154, 1)")

color4_fill <- c("rgba(59, 134, 134, 0.5)", "rgba(121, 189, 154, 0.5)", 
                 "rgba(168, 219, 168, 0.5)", "rgba(207, 240, 158, 0.5)")
color4_line <- c("rgba(59, 134, 134, 1)", "rgba(121, 189, 154, 1)", 
                 "rgba(168, 219, 168, 1)", "rgba(207, 240, 158, 1)")

color8_fill <- c("rgba(38, 123, 123, 0.5)", "rgba(59, 134, 134, 0.5)", 
                 "rgba(92, 167, 142, 0.5)", "rgba(121, 189, 154, 0.5)", 
                 "rgba(147, 204, 160, 0.5)", "rgba(168, 219, 168, 0.5)", 
                 "rgba(190, 227, 163, 0.5)", "rgba(207, 240, 158, 0.5)")
color8_line <- c("rgba(38, 123, 123, 1)", "rgba(59, 134, 134, 1)", 
                 "rgba(92, 167, 142, 1)", "rgba(121, 189, 154, 1)", 
                 "rgba(147, 204, 160, 1)", "rgba(168, 219, 168, 1)", 
                 "rgba(190, 227, 163, 1)", "rgba(207, 240, 158, 1)")
color8_hex <- c("#064547","#0B686B","#267B7B","#3B8686","#5CA78E","#79BD9A", 
                "#93CCA0","#A8DBA8","#BEE3A3","#CFF09E","#E8F8C9","#F8FFD9")




# Dark layout
dark_layout <- function(p) {
  layout(
    p,
    paper_bgcolor = '#1e1e1e',
    plot_bgcolor = '#2c2c2c',
    font = list(color = 'white'),
    xaxis = list(color = 'white'),
    yaxis = list(color = 'white')
  )
}
```

# Customer Overview

<!-- thông tin nhân khẩu học, phân phối thu nhập, tuổi 
  Cột 1:  Violin của Income, Age
          
-->

Column {data-width=350}
-----------------------------------------------------------------------
### Age
```{r}
ifood_df %>% select(Year_Birth) %>% 
  mutate(Age = 2020 - Year_Birth) %>% 
  filter(Age <= 100) %>% 
  plot_ly(y = ~Age, type = "violin", 
          box = list(visible = T),
          quartilemethod="linear",
          meanline = list(visible = T), 
          line = list(color = "rgba(38, 123, 123, 1)"),
          fillcolor = "rgba(38, 123, 123, 0.5)", 
          x0 = "Age",
          points = "all",
          jitter = 0,
          marker = list(color = "rgba(38, 123, 123)")) %>% 
  layout(yaxis = list(title = "", zeroline = F)) %>% 
  dark_layout()
```

### Kid and Teen

```{r}
KidTeen <- ifood_df %>% select(Kidhome, Teenhome) %>% 
  mutate(Total = Kidhome + Teenhome) %>% 
  group_by(Total) %>% 
  summarise(count = n()) %>% 
  mutate(percent = paste0(round(count/sum(count)*100, 2), "%"))
plot_ly(data = KidTeen, x = ~Total, y = ~count, type = "bar", 
        text = KidTeen$percent,
        marker = list(color = color4_line)) %>% 
  layout(xaxis = list(title = "Total number of children and teen"),
         yaxis = list(title = "")) %>% 
  dark_layout()
```


Column {data-width=650, .tabset}
-----------------------------------------------------------------------
### Income
```{r}
ifood_df %>% 
  plot_ly(y = ~Income, type = "violin", 
          box = list(visible = T),
          quartilemethod="linear",
          meanline = list(visible = T), 
          line = list(color = "rgba(38, 123, 123, 1)"),
          fillcolor = "rgba(38, 123, 123, 0.5)", 
          x0 = "Income",
          points = "all",
          jitter = 0,
          marker = list(color = "rgba(38, 123, 123)")) %>% 
  layout(yaxis = list(title = "", zeroline = F)) %>% 
  dark_layout()
```

### Income by Marital
```{r}
name <- sort(unique(ifood_df$Marital_Status))
fig <- plot_ly()
for (i in 1:length(name)){
  temp_df <- ifood_df %>% filter(Marital_Status == name[i])
  fig <- fig %>% 
    add_trace(data = temp_df,
              y = ~Income,
              type = "violin", name = name[i],
              box = list(visible = TRUE), 
              meanline = list(visible = TRUE),
              quartilemethod = "linear", 
              points = "all", jitter = 0,
              line = list(color = color8_line[i]), 
              fillcolor = color8_fill[i],
              marker = list(color = color8_line[i]))
}
fig %>% layout(xaxis = list(title = "Marital status"),
               yaxis = list(zeroline = FALSE)) %>% dark_layout()
```

### Income by Education
```{r}
name <- sort(unique(ifood_df$Education))
fig <- plot_ly()
for (i in 1:length(name)){
  temp_df <- ifood_df %>% filter(Education == name[i])
  fig <- fig %>% 
    add_trace(data = temp_df,
              y = ~Income,
              type = "violin", name = name[i],
              box = list(visible = TRUE), 
              meanline = list(visible = TRUE),
              quartilemethod = "linear", 
              points = "all", jitter = 0,
              line = list(color = color8_line[i]), 
              fillcolor = color8_fill[i],
              marker = list(color = color8_line[i]))
}
fig %>% layout(xaxis = list(title = "Education"),
               yaxis = list(zeroline = FALSE)) %>% dark_layout()
```


# Spending Behavior
Column {data-width=350}
-----------------------------------------------------------------------
### Expenditure share of products
```{r}
pie <- data.frame(ifood_df %>% 
                    select(MntWines, MntFruits, MntMeatProducts,
                    MntFishProducts, MntSweetProducts, 
                    MntGoldProds) %>%
  apply(2, sum))
pie <- `colnames<-` (pie, "Sum")
pie <- `rownames<-` (pie, c("Wines Products", "Fruits Products",
                            "Meat Products", "Fish Products",
                            "Sweet Products", "Gold Products"))
pie <- sort_by.data.frame(pie, y = pie$Sum)

plot_ly(pie, labels = ~rownames(pie),values = ~Sum, type = "pie",
        textposition = 'inside',
        textinfo = 'label+percent',
        marker = list(colors = color8_line[nrow(pie):1],
                      line = list(color = '#FFFFFF', width = 1)),
        showlegend = FALSE) %>% 
  dark_layout()

```

### Products by average spend
```{r}
bar <- data.frame(ifood_df %>% 
                    select(MntWines, MntFruits, MntMeatProducts,
                    MntFishProducts, MntSweetProducts, 
                    MntGoldProds) %>%
  apply(2, mean))
bar <- `colnames<-` (bar, "Mean")
bar <- `rownames<-` (bar, c("Wines", "Fruits","Meat", "Fish",
                            "Sweet", "Gold"))

plot_ly(bar, x = ~rownames(bar), y = ~round(Mean, 2), type = "bar",
        marker = list(color = color8_line[6:1]),
        showlegend = FALSE) %>% 
  layout(xaxis = list(title = "Products"),
         yaxis = list(title = "Average amount level")) %>% 
  dark_layout()
```


Column {data-width=650, .tabset}
-----------------------------------------------------------------------
### MntTotal and Income
```{r}
ifood_df %>% mutate(MntTotal = MntWines + MntFruits + MntMeatProducts +
                      MntFishProducts + MntSweetProducts + MntGoldProds) %>% 
  plot_ly(x = ~Income, y = ~MntTotal,
          marker = list(color = color8_line[1])) %>% 
  layout(xaxis = list(title = "Total amount for all products")) %>% 
  dark_layout()
```

### MntTotal and Marital
```{r}
name <- sort(unique(ifood_df$Marital_Status))
fig <- plot_ly()
for (i in 1:length(name)){
  temp_df <- ifood_df %>% 
    mutate(MntTotal = MntWines + MntFruits + MntMeatProducts +
                      MntFishProducts + MntSweetProducts + MntGoldProds) %>% 
    filter(Marital_Status == name[i])
  fig <- fig %>% 
    add_trace(data = temp_df,
              y = ~MntTotal,
              type = "violin", name = name[i],
              box = list(visible = TRUE), 
              meanline = list(visible = TRUE),
              quartilemethod = "linear", 
              points = "all", jitter = 0,
              line = list(color = color8_line[i]), 
              fillcolor = color8_fill[i],
              marker = list(color = color8_line[i]))
}
fig %>% layout(xaxis = list(title = "Marital Status"),
               yaxis = list(zeroline = FALSE)) %>% dark_layout()
```

### MntTotal and Education
```{r}
name <- sort(unique(ifood_df$Education))
fig <- plot_ly()
for (i in 1:length(name)){
  temp_df <- ifood_df %>% 
    mutate(MntTotal = MntWines + MntFruits + MntMeatProducts +
                      MntFishProducts + MntSweetProducts + MntGoldProds) %>% 
    filter(Education == name[i])
  fig <- fig %>% 
    add_trace(data = temp_df,
              y = ~MntTotal,
              type = "violin", name = name[i],
              box = list(visible = TRUE), 
              meanline = list(visible = TRUE),
              quartilemethod = "linear", 
              points = "all", jitter = 0,
              line = list(color = color8_line[i]), 
              fillcolor = color8_fill[i],
              marker = list(color = color8_line[i]))
}
fig %>% layout(xaxis = list(title = "Education"),
               yaxis = list(zeroline = FALSE)) %>% dark_layout()
```


# Purchase Channels
Column {data-width=350}
-----------------------------------------------------------------------
### Purchase channel by Age
```{r}
ifood_df %>% 
  select(Year_Birth, 
         NumWebPurchases, NumCatalogPurchases, NumStorePurchases) %>% 
  mutate(Age = 2020 - Year_Birth) %>% 
  filter(Age <= 100) %>% 
  group_by(Age) %>% 
  summarise(web = sum(NumWebPurchases), 
            catalog = sum(NumCatalogPurchases),
            store = sum(NumStorePurchases)) %>% 
  plot_ly(x = ~Age, y = ~web, name = "Web",
          type = "scatter", mode = "lines",
          line = list(color = color4_line[1]),
          marker = list(color = color4_line[1])) %>% 
  add_trace(y = ~catalog, name = "Catalog",
            line = list(color = color4_line[2]),
            marker = list(color = color4_line[2])) %>% 
  add_trace(y = ~store, name = "Store",
            line = list(color = color4_line[3]),
            marker = list(color = color4_line[3])) %>% 
  layout(yaxis = list(title = "Total number of Purchase")) %>% 
  dark_layout()
```

### Website efficiency
```{r}
ifood_df %>% select(NumWebVisitsMonth, NumWebPurchases) %>% 
  summarise(data.frame(
    stage = c("Visits", "Purchases"),
    value = c(sum(NumWebVisitsMonth), sum(NumWebPurchases)))
    ) %>% 
  plot_ly(type = "funnel", x = ~value, y = ~stage,
          textinfo = "value+percent previous+percent initial",
          marker = list(color = color2_line,
                        line = list(width = 1, color = "#fff")),
          connector = list(line = list(color = "#fff", dash = "soild", 
                                       width = 3))) %>% 
  layout(yaxis = list(title = "", categoryarray = stage)) %>% 
  dark_layout()
```


Column {data-width=650, .tabset}
-----------------------------------------------------------------------
### Purchase channel
```{r}
ifood_df %>% 
  select(NumWebPurchases, NumCatalogPurchases, NumStorePurchases) %>% 
  summarise(web = sum(NumWebPurchases), 
            catalog = sum(NumCatalogPurchases),
            store = sum(NumStorePurchases)) %>% 
  plot_ly(x = "Web" ,y = ~web, type = "bar",
          text = ~web,
          marker = list(color = color4_line[1]),
          showlegend = FALSE) %>% 
  add_trace(y = ~catalog, x = "Catalog",
            text = ~catalog,
            marker = list(color = color4_line[2]),
            showlegend = FALSE) %>% 
  add_trace(y = ~store, x = "Store",
            text = ~store,
            marker = list(color = color4_line[3]), 
            showlegend = FALSE) %>% 
  layout(yaxis = list(title = "Total number of Purchases"),
         barmode = "group") %>% 
  dark_layout()
```

### Purchase channel by Education
```{r}
ifood_df %>% 
  select(Education,
         NumWebPurchases, NumCatalogPurchases, NumStorePurchases) %>% 
  group_by(Education) %>% 
  summarise(web = sum(NumWebPurchases), 
            catalog = sum(NumCatalogPurchases),
            store = sum(NumStorePurchases)) %>% 
  plot_ly(x = ~Education, y = ~web, type = "bar", name = "Web",
          text = ~web,
          marker = list(color = color4_line[1])) %>% 
  add_trace(y = ~catalog, name = "Catalog",
            text = ~catalog,
            marker = list(color = color4_line[2])) %>% 
  add_trace(y = ~store, name = "Store",
            text = ~store,
            marker = list(color = color4_line[3])) %>% 
  layout(yaxis = list(title = "Total number of Purchases"), 
         # y = list(title = "Edu")
         barmode = "group") %>% 
  dark_layout()
```

### Purchases channel by Marital
```{r}
ifood_df %>% 
  select(Marital_Status,
         NumWebPurchases, NumCatalogPurchases, NumStorePurchases) %>% 
  group_by(Marital_Status) %>% 
  summarise(web = sum(NumWebPurchases), 
            catalog = sum(NumCatalogPurchases),
            store = sum(NumStorePurchases)) %>% 
  plot_ly(x = ~Marital_Status, y = ~web, type = "bar", name = "Web",
          text = ~web,
          marker = list(color = color4_line[1])) %>% 
  add_trace(y = ~catalog, name = "Catalog",
            text = ~catalog,
            marker = list(color = color4_line[2])) %>% 
  add_trace(y = ~store, name = "Store", 
            text = ~store,
            marker = list(color = color4_line[3])) %>% 
  layout(yaxis = list(title = "Total number of Purchases"), 
         xaxis = list(title = "Marital status"),
         barmode = "group") %>% 
  dark_layout()
```


# Marketing Campaign
Column {data-width=350}
-----------------------------------------------------------------------
### Customers accepted in at least 1 campaign
```{r}
ifood_df %>% select(AcceptedCmp1, AcceptedCmp2, AcceptedCmp3, 
                    AcceptedCmp4, AcceptedCmp5) %>% 
  mutate(Accepted = AcceptedCmp1 + AcceptedCmp2 + AcceptedCmp3 + 
                    AcceptedCmp4 + AcceptedCmp5) %>% 
  summarise(paste0(round(sum(Accepted)/ nrow(ifood_df)*100, 3), "%")) %>% 
  valueBox(format(paste0(), big.mark = ",", decimal.mark = "."),
           caption = "Customers accepted in at least 1 campaign",
           icon = "fa-solid fa-percent",
           color = color8_line[8])
```

### KPI
```{r}
ifood_df %>% 
  summarise(Campaign = c("Campaign1", "Campaign2", "Campaign3", 
                         "Campaign4", "Campaign5", "Response"),
            Accepted = c(sum(AcceptedCmp1), sum(AcceptedCmp2), 
                         sum(AcceptedCmp3), sum(AcceptedCmp4),
                         sum(AcceptedCmp5), sum(Response)),
            No_Accepted = c(sum(AcceptedCmp1-1)*-1, sum(AcceptedCmp2-1)*-1, 
                         sum(AcceptedCmp3-1)*-1, sum(AcceptedCmp4-1)*-1,
                         sum(AcceptedCmp5-1)*-1, sum(Response-1)*-1)) %>% 
  plot_ly(x = ~Campaign) %>%
  add_trace(y = ~Accepted, type = "bar", name = "Accepted",
            text = ~Accepted,
            marker = list(color = color4_line[1])) %>% 
  add_trace(y = ~No_Accepted, type = "bar", name = "No Accepted",
            text = ~No_Accepted,
            marker = list(color = color4_line[2])) %>% 
  layout(yaxis = list(title = ""), barmode = "stack") %>% 
  dark_layout()
```


Column {data-width=650, .tabset}
-----------------------------------------------------------------------
### Response Rate by Age & Income
```{r}
ifood_df %>% select(Year_Birth, Income, Response) %>% 
  mutate(Age = 2020 - Year_Birth) %>% 
  filter(Age <= 100) %>% 
  mutate(Income_gr = case_when(Income <= 10000 ~ "<= 10000",
                               Income <= 30000 ~ "10001 - 30000",
                               Income <= 100000 ~ "30001 - 100000",
                               Income <= 300000 ~ "100001 - 300000",
                               Income > 300000 ~ "> 300000"),
         Age_gr = case_when(Age <= 29 ~ "24 - 29", Age <= 34 ~ "30 - 34",
                            Age <= 39 ~ "35 - 39", Age <= 44 ~ "40 - 44",
                            Age <= 49 ~ "45 - 49", Age <= 54 ~ "50 - 54",
                            Age <= 59 ~ "55 - 59", Age <= 64 ~ "60 - 64",
                            Age <= 69 ~ "65 - 69", Age <= 74 ~ "70 - 74",
                            Age <= 79 ~ "75 - 80", Age > 80 ~ "80+")) %>% 
  group_by(Income_gr, Age_gr) %>% 
  summarise(total = n(),
            sum_res = sum(Response),
            Percent = round(sum_res/total*100,2)) %>% 
  select(Income_gr, Age_gr, Percent) %>% 
  plot_ly(x = ~Age_gr, y = ~Income_gr, z = ~Percent, type = "heatmap") %>% 
  layout(xaxis = list(title = "Age group"),
         yaxis = list(title = "Income group",
                      categoryarray = c("<= 10000", "10001 - 30000", 
                                        "30001 - 100000", "100001 - 300000",
                                        "> 300000"))) %>% 
  dark_layout()
  
```


# Customer Segmentation
Column {data-width=1000, .tabset}
-----------------------------------------------------------------------
### 6 Cluster
```{r}
library(factoextra)
# Lọc dữ liệu
cluster_df <- ifood_df %>%
  mutate(Age = 2020 - Year_Birth) %>%
  filter(Age <= 100) %>% 
  mutate(Basic = ifelse(Education == "Basic", 1, 0),
         town_Cycle = ifelse(Education == "2n Cycle", 1, 0),
         Graduation = ifelse(Education == "Graduation", 1, 0),
         Master = ifelse(Education == "Master", 1, 0),
         Single = ifelse(Marital_Status == "Single" |
                           Marital_Status == "Alone" |
                           Marital_Status == "YOLO", 1, 0),
         Married = ifelse(Marital_Status == "Married", 1, 0),
         Divorced = ifelse(Marital_Status == "Divorced", 1, 0),
         Widow = ifelse(Marital_Status == "Widow", 1, 0),
         Together = ifelse(Marital_Status == "Together", 1, 0),
         Time = as.numeric(difftime("2022-12-31", Dt_Customer))) %>% 
  select(-Year_Birth, -Dt_Customer, -Education, -Marital_Status) %>%
  scale()

# PCA
pca <- prcomp(cluster_df)
# get_eig(pca)

# Tạo K-mean
cl <- kmeans(cluster_df, 6)

# pca_data <- as.data.frame(pca$x[, 1:3])
# pca_data$cluster <- factor(cl$cluster)
# pca_data %>% plot_ly(x = ~PC1, y = ~PC2, z = ~PC3,
#                      color = ~cluster)

ifood_df %>%
  mutate(Age = 2020 - Year_Birth) %>%
  filter(Age <= 100) %>%
  plot_ly(x = ~Income, y = ~MntWines, type = "scatter",
          text = ~paste("Cluster: ", cl$cluster),
          color = ~factor(cl$cluster),
          colors = color8_hex[1:6]) %>% 
  dark_layout()
```

### 12 Cluster
```{r}
cl <- kmeans(cluster_df, 12)
ifood_df %>%
  mutate(Age = 2020 - Year_Birth) %>%
  filter(Age <= 100) %>%
  plot_ly(x = ~Income, y = ~MntWines, type = "scatter",
          text = ~paste("Cluster: ", cl$cluster),
          color = ~factor(cl$cluster),
          colors = color8_hex) %>% 
  dark_layout()
```


<!-- # Dash 1 -->
<!-- Column {data-width=350} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Chart A -->

<!-- ```{r} -->
<!-- ifood_df %>%  -->
<!--   plot_ly(y = ~Income, type = "violin",  -->
<!--           box = list(visible = T), -->
<!--           quartilemethod="linear", -->
<!--           meanline = list(visible = T),  -->
<!--           line = list(color = "rgba(38, 123, 123, 1)"), -->
<!--           fillcolor = "rgba(38, 123, 123, 0.5)",  -->
<!--           x0 = "Income", -->
<!--           points = "all", -->
<!--           jitter = 0, -->
<!--           marker = list(color = "rgba(38, 123, 123)")) %>%  -->
<!--   layout(yaxis = list(title = "", zeroline = F)) %>%  -->
<!--   dark_layout() -->
<!-- ``` -->

<!-- ### Chart B -->

<!-- ```{r} -->
<!-- ifood_df %>%  -->
<!--   plot_ly(y = ~Recency, type = "violin",  -->
<!--           box = list(visible = T), -->
<!--           meanline = list(visible = T),  -->
<!--           line = list(color = "rgba(59, 134, 134, 1)"), -->
<!--           fillcolor = "rgba(59, 134, 134, 0.5)",  -->
<!--           x0 = "Number of days", -->
<!--           points = "all", -->
<!--           jitter = 0, -->
<!--           marker = list(color = "rgba(59, 134, 134, 1)")) %>%  -->
<!--   layout(yaxis = list(title = "Days since last purchase", zeroline = F)) %>%  -->
<!--   dark_layout() -->
<!-- ``` -->

<!-- Column {data-width=650} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ### Chart C -->

<!-- ```{r} -->
<!-- ifood_df %>% select(MntMeatProducts, MntWines) %>% -->
<!--   plot_ly() %>%  -->
<!--   add_trace(type = "violin", y = ~MntMeatProducts, name = "Meat", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color2_line[1]), fillcolor = color2_fill[1], -->
<!--             points = "all", jitter = 0, -->
<!--             marker = list(color = color2_fill[1])) %>%  -->
<!--   add_trace(type = "violin", y = ~MntWines, name = "Wine", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color2_line[2]), fillcolor = color2_fill[2], -->
<!--             points = "all", jitter = 0, -->
<!--             marker = list(color = color2_fill[2])) %>%  -->
<!--   layout(xaxis = list(title = "Products"), -->
<!--          yaxis = list(title = "Amount", zeroline = FALSE)) %>%  -->
<!--   dark_layout() -->
<!-- ``` -->

<!-- ### Chart D -->

<!-- ```{r} -->
<!-- ifood_df %>% select(MntFishProducts, MntFruits, MntGoldProds, MntSweetProducts) %>%  -->
<!--   plot_ly() %>%  -->
<!--   add_trace(type = "violin", y = ~MntFishProducts, name = "Fish", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color4_line[1]), fillcolor = color4_fill[1], -->
<!--             points = "all", jitter = 0, # add point -->
<!--             marker = list(color = color4_fill[1])) %>%  -->
<!--   add_trace(type = "violin", y = ~MntFruits, name = "Fruits", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color4_line[2]), fillcolor = color4_fill[2], -->
<!--             points = "all", jitter = 0, -->
<!--             marker = list(color = color4_fill[2])) %>%  -->
<!--   add_trace(type = "violin", y = ~MntGoldProds, name = "GoldProds", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color4_line[3]), fillcolor = color4_fill[3], -->
<!--             points = "all", jitter = 0, -->
<!--             marker = list(color = color4_fill[3])) %>%  -->
<!--   add_trace(type = "violin", y = ~MntSweetProducts, name = "Sweet", -->
<!--             box = list(visible = TRUE), meanline = list(visible = TRUE), -->
<!--             line = list(color = color4_line[4]), fillcolor = color4_fill[4], -->
<!--             points = "all", jitter = 0, -->
<!--             marker = list(color = color4_fill[4])) %>%  -->
<!--   layout(xaxis = list(title = "Products"), -->
<!--          yaxis = list(title = "Amount", zeroline = FALSE)) %>%  -->
<!--   dark_layout() -->
<!-- ``` -->


<!-- Column {data-width=330} -->
<!-- ----------------------------------------------------------------------- -->

